Self Regulation Ontology Retest Data Report

### 2017-04-18 SRO_Report.Rmd
changed box plots of differences

t1_2_difference = merge(t1_2_difference, comp_dates[,c('sub_id', 'days_btw')], by='sub_id')
str(t1_2_difference)
```

@@

Box plots showing the distribution of difference scores for each task

```{r fig.width=20}
t1_2_difference %>%
  ggplot(aes(dv, difference))+
  geom_boxplot()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

>>>>

t1_2_difference = merge(t1_2_difference, comp_dates[,c('sub_id', 'days_btw')], by='sub_id')
```

@@

To confirm the slope of this line is not significant. That is, there doesn't seem to be a systematic difference between the two measurements depending on the number of days between the two measurements.

```{r warning=FALSE, message=FALSE}
summary(lm(mean_diff ~ days_btw, data=tmp))
```

For reference here are the box plots showing the distribution of difference scores for each task.

```{r warning=FALSE, message=FALSE, fig.height=36}
ggplotly(t1_2_difference %>%
           ggplot(aes(dv, difference, label=dv))+
           geom_boxplot()+
           theme_bw()+
           coord_flip()+
           xlab("")+
           ylab("Standardized difference")
)
```
